Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-08-14 tex/sections/intro.tex
Add explanation about safeguard chains in CH1
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance system
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the Argennon blockchain.
Each minted block is required to get approved by its corresponding validator committee.
Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the system.
Every committee of validators has an index between $0$ and $m - 1$, and is resposible for validating block number $n$,
if $n$ modulo $m$ equals the committee index. A block is approved if it takes approval votes from at least $2/3$ of
the total stake of its validator committee.

@@

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
the final ledger state of the block. The CI set defines how the final ledger state of the block can be reached from
the state of its previous block via a set of intermediate states.
Each individual CI statement defines an ordered list of external requests\footnote{External requests in Argennon are
similar to transactions in older blockchains.} and determines the state before and after executing those requests:
\[
    \tau_{(s_i,s_{i+1},\mathbb{R})} \coloneqq \text{``$s_{i+1}$ is the next state after executing external requests
        $\mathbb{R}$ on state $s_i$''}
\]
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud. They can also receive the state of the previous
block (the required part of it) and proofs that show the received data is consistent with the previous block commitment.

@@

>>>>

To overcome these difficulties, Argennon\footnote{The classical pronunciation should be used:\textipa{/Ar"gen.non/}}
uses a Hybrid Proof of Stake consensus protocol, which is
capable of combining the benefits of a centralized and a decentralized system. A small committee of
delegates is democratically elected by users via the Argennon Decentralized Autonomous Governance system
(ADAGs). This committee usually\footnote{The election term and the number of committee members can be changed by the
ADAGs.} is elected for a one-year term, has five members, and is responsible for minting new
blocks of the Argennon blockchain.
Each minted block is required to get approved by its corresponding validator committee.
Validator committees are very
large sets of validators including at least three percent of the maximum possible stake of the system.
Every committee of validators has an index between $0$ and $m - 1$, and is responsible for validating block number $n$,
if $n$ modulo $m$ equals the committee index. A block is approved if it takes approval votes from at least $2/3$ of
the total stake of its validator committee.

@@

Each block of the Argennon blockchain contains a set of Computational Integrity (CI) statements and a commitment to
the final ledger state of the block (i.e.\ the ledger state after executing all transactions of the block). The CI
set defines how the final state of the block can be reached from
the state of its previous block via a set of intermediate states.
Each individual CI statement defines an ordered list of external requests\footnote{External requests in Argennon are
similar to transactions in older blockchains.} and determines the state before and after executing those requests:
\[
    \tau_{(s_i,s_{i+1},\mathbb{R})} \coloneqq \text{``$s_{i+1}$ is the next state after executing external requests
        $\mathbb{R}$ on state $s_i$''}
\]
Validators can\footnote{Using the Argennon cloud is optional for a validator.} receive succinct cryptographic proofs
of these CI statements (STARK/SNARK) from the Argennon cloud. They can also receive the state of the previous
block (the required part of it) and proofs that show the received data is consistent with the previous block commitment.

@@

Using succinct argument of knowledge systems makes an Argennon validator light enough to be implemented as a smart
contract. By deploying an Argennon validator on another turing complete smart contract platform, Argennon could use
more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet.
